---
title: "Working with episodes data with episoder"
author: "Adam Celejewski"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_episorder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Introdcution
Behavioural data, such feeding or drinking recordings, can be broken down into discrete units of activity, or episodes. A common starting point for the analysis of episode data involves the examination of the inter-event interval information.

The episoder package provides several functions to aid in the extraction of relevant episode information form time-series event data sets according a specified inter-event interval of occurrence. The output of these functions can than be subjected to further analysis.


## Package Info

Episoder functions are built with both, functions from the [dplyr](https://cran.r-project.org/web/packages/dplyr/index.html)
 package  as well as their base R equivalents. Episoder functions that do not utilize dplyr are denoted by the `_base` suffix.

The dplyr-based functions can be applied across groups and  accept grouping variables such as subject ID or session ID. This functionality was implemented with `dplyr::group_by`   rather than with base R alternatives such as `base::tapply` as the dplyr implementation is significantly faster for larger data sets.

Although this example uses tibble class objects in place of the data fame, (see [tibbles](https://cran.r-project.org/web/packages/tibble/vignettes/tibble.html)), traditional data frames are also accepted. 


## Data Format

The episoder package requires data to be organized in long-format format as illustrated in the included data file `lickometer`.

```{r, 'data format'}
lickometer
```

This data contains lickometer recordings (recordings of individual licks) from 16 rats drinking sucrose solutions in two separate treatment conditions (see `?lickometer` for further details). Two pieces of information must be provided. A column of event times, in this case of the example at a 20ms sampling resolution, and one more grouping variables such as subject ID, session ID, etc.



##Extracting episode 
Episoder functions are but around two core functions `episdode_summarize` and `epsode_label`


episode_label demarcates and arranges episdoes accoridng to a speici
the lenght of the the. This data be used to for further sumiraiztion, or to fit mdoels

episode_summaraize provides a summary of according to the specified number of events per episode and proiveds a summary of episode paramters including events per episode 

```{r, episode lable}
plot(1:10)
plot(10:1)
```




## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.
