---
title: "identifying episodes episoder"
author: "Adam Celejewski"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_episorder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Behavioural data such feeding or drinking can be broken down into discrete units of activity, or episodes. A common starting point for the analysis of episode data involves the examination of the inter-event interval information.

The episoder package provides several functions for to aid in the extraction of relevant episode information form time-series event datasets according a specified inter-event interval of occurrence and/or the number of events per episodes. The the output of these functions can than be subjected to further analysis.


## Vignette Info

Note that this example useses the tibble an extension of the datafame , (tbl_df class;  see https://cran.r-project.org/web/packages/tibble/vignettes/tibble.html), but tradtional data frames are also accepted. 



## Data input

The funtions require data to organzied in long-format format as illustrated in data file example. This data contains Lickometer recordings (recordings of invidual licks) from 16 rats drinking sucrsoe solutions in two spereate treatment conditons. Two pices of information are requiured. A column of event times likcs_df time,  and column in this case of the example at a 20ms sampling resolution, the invidual level of analsys such as licksdf subject and licksdf$esession. Any number of columns providing can be inclueded  that will berequired for further analays of the data. 



##Identifying 
```{r, 'event time'}
data("lickometer")

```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.
